Measurement and Probability in Fuzzy Quantum Theories

### 2017-03-07 prop_iop.tex
prop_iop.tex \section{Contextuality and the Born Rule in Fuzzy Quantum Theories} Updating...

Given any sub-event space~$\events'\subseteq\events$, in order to
qualify how well-behaved a quantum interval-valued probability measure~$\bar{\mu}:\events'\rightarrow\mathscr{I}$
could be, we introduce a notation of core.

@@

In the rest of the letter, we will provide examples of quantum interval-valued
probability measures on $\events_{24}$, and show how a quantum interval-valued
probability measure~$\bar{\mu}:\events_{24}\rightarrow\mathscr{I}$
could be depending on different intervals~$\mathscr{I}$.

>>>>

Given any sub-event space~$\events'\subseteq\events$, in order to
qualify how well-behaved a quantum interval-valued probability measure~$\bar{\mu}:\events'\rightarrow\mathscr{I}$
could be, we introduce the notion of core.

@@

\noindent In the rest of the letter, we will provide examples of quantum
interval-valued probability measures on $\events_{24}$, and show
how a quantum interval-valued probability measure~$\bar{\mu}:\events_{24}\rightarrow\mathscr{I}$
could be depending on different intervals~$\mathscr{I}$.
